Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Explain no_duplicate

\subsubsection{no\_duplicate}
\label{subs:no_duplicate}

>>>>

\subsubsection{no\_duplicate}
\label{subs:no_duplicate}
There should rarely be duplicate commit messages (except for automatic messages like merges). A duplicate commit message hints at a duplicate change to the code and makes reading git logs more difficult (for humans).

If a commit has the same commit message as a commit that has been processed before, this test fails.
